---
output: 
  pdf_document:
      latex_engine: xelatex
mainfont: Verdana
theme: united
always_allow_html: yes

header-includes:
    - \usepackage{fancyhdr}
    - \usepackage{hyperref}
    - \usepackage{graphicx}
    - \hypersetup{linkcolor = blue}
    - \pagestyle{fancy}
    - \fancyhead[LE,RO]{© More Than Ideas}
    - \fancyhead[LE,LO]{\thepage}
---

\thispagestyle{empty}
\begin{center}
\includegraphics[width=10cm,height=10cm]{"www/morethanideas.jpeg"}
\end{center}

\vspace{4cm}

\begin{center}
{\Huge `r eventSelect`}

\vspace{0.3cm}

{`r paste0(format(Sys.Date(),"%B %d"),", ", format(Sys.Date(),"%Y"))`}

\end{center}
\newpage

\tableofcontents

\newpage

```{r,echo = FALSE}

    if(eventSelect == "Pauline Hanson Comments"){
      date <- "2016-11-28"
    }
    if(eventSelect == "Linda Burney Elected"){
      date <- "2016-08-30" 
    }
    if(eventSelect == "Closing the Gap Report"){
      date <- "2016-02-10"
    }
    
    db.before <- db[grep(paste0(seq(as.Date(date) - 8,as.Date(date) - 1,"days"),collapse = "|"),db$COMMENT_CREATED),]
    db.day <- db[which(db$COMMENT_CREATED == date),]
    db.after <- db[grep(paste0(seq(as.Date(date) + 1,as.Date(date) + 8,"days"),collapse = "|"),db$COMMENT_CREATED),]
    db.period <- db[grep(paste0(seq(as.Date(date) - 8,as.Date(date) + 8,"days"),collapse = "|"),db$COMMENT_CREATED),]
    
    period_frequencies <- as.data.frame(table(db.period$COMMENT_CREATED))
    colnames(period_frequencies) <- c("Date","Frequency")
    
    ### ===============
    
    ## BEFORE 
    
    ## ================
    
    before.comments <- db.before$COMMENT
    
    comments <- paste(" ",paste(before.comments,collapse = " ")," ")
    comments <- gsub("[[:punct:]]|[0-9]","",comments)
    comments <- tolower(comments)
    
    comments_string <- paste0(" ",comments," ")
    comments <- strsplit(comments," ")
    
    ## MAKE THE KEYWORD TABLE
    kw.tab.before <- table(comments)
    kw.tab.before <- as.data.frame(kw.tab.before)
    kw.tab.before$comments <- gsub("\n","",kw.tab.before$comments)
    
    ## REMOVE STOPWORDS
    stopwords <- gsub("[[:punct:]]","",stopwords("en"))
    kw.remove <- c()
    for(ii in 1:length(stopwords)){
      if(any(kw.tab.before$comments == stopwords[ii])){
        kw.remove <- c(kw.remove,which(kw.tab.before$comments == stopwords[ii]))
      }
    }
    
    count.before <- c()
    for(ii in 1:length(keywords)){
      count.before[ii] <- 0
      for(aa in 1:length(keywords[[ii]])){
        count.before[ii] <- count.before[ii] + str_count(comments_string,as.character(keywords[[ii]][aa]))
      }
    }

    countdf.before <- data.frame(count.before,kwList$Placeholder)
    colnames(countdf.before) <- c("kwCount","kw")

    countdf.before <- countdf.before[order(-countdf.before$kwCount),]

    if(any(countdf.before$kwCount == 0)){
      countdf.before <- countdf.before[-which(countdf.before$kwCount == 0),]
    }
    colnames(countdf.before) <- c("Frequency","Theme")
    
    countdf.before <- countdf.before[1:20,]
    
    kw.tab.before <- kw.tab.before[-kw.remove,]
    
    kw.tab.before <- kw.tab.before[order(-kw.tab.before$Freq),]
    
    kw.tab.before$comments <- gsub("\\s+","",kw.tab.before$comments)
    kw.tab.before <- kw.tab.before[-which(kw.tab.before$comments == ""),]
    
    kw.tab.before <- kw.tab.before[1:20,]
    
    colnames(kw.tab.before) <- c("Comment","Frequency")
    
    substr(kw.tab.before$Comment,1,1) <- toupper(substr(kw.tab.before$Comment,1,1))
    
    ## =========
    
    ##   DAY
    
    ## =========
    
    day.comments <- db.day$COMMENT
    
    comments <- paste(" ",paste(day.comments,collapse = " ")," ")
    comments <- gsub("[[:punct:]]|[0-9]","",comments)
    comments <- tolower(comments)
    
    comments_string <- paste0(" ",comments," ")
    comments <- strsplit(comments," ")
    
    ## MAKE THE KEYWORD TABLE
    kw.tab.day <- table(comments)
    kw.tab.day <- as.data.frame(kw.tab.day)
    kw.tab.day$comments <- gsub("\n","",kw.tab.day$comments)
    
    ## REMOVE STOPWORDS
    stopwords <- gsub("[[:punct:]]","",stopwords("en"))
    kw.remove <- c()
    for(ii in 1:length(stopwords)){
      if(any(kw.tab.day$comments == stopwords[ii])){
        kw.remove <- c(kw.remove,which(kw.tab.day$comments == stopwords[ii]))
      }
    }
    
    count.day <- c()
    for(ii in 1:length(keywords)){
      count.day[ii] <- 0
      for(aa in 1:length(keywords[[ii]])){
        count.day[ii] <- count.day[ii] + str_count(comments_string,as.character(keywords[[ii]][aa]))
      }
    }

    countdf.day <- data.frame(count.day,kwList$Placeholder)
    colnames(countdf.day) <- c("kwCount","kw")
    
    countdf.day <- countdf.day[1:20,]

    countdf.day <- countdf.day[order(-countdf.day$kwCount),]

    if(any(countdf.day$kwCount == 0)){
      countdf.day <- countdf.day[-which(countdf.day$kwCount == 0),]
    }
    colnames(countdf.day) <- c("Frequency","Theme")
    
    kw.tab.day <- kw.tab.day[-kw.remove,]
    
    kw.tab.day <- kw.tab.day[order(-kw.tab.day$Freq),]
    
    kw.tab.day$comments <- gsub("\\s+","",kw.tab.day$comments)
    kw.tab.day <- kw.tab.day[-which(kw.tab.day$comments == ""),]
    
    kw.tab.day <- kw.tab.day[1:20,]
    
    colnames(kw.tab.day) <- c("Comment","Frequency")
    
    substr(kw.tab.day$Comment,1,1) <- toupper(substr(kw.tab.day$Comment,1,1))
    
    
    
    ## ========================
    ##           AFTER
    ## ========================
    
    after.comments <- db.after$COMMENT
    
    comments <- paste(" ",paste(after.comments,collapse = " ")," ")
    comments <- gsub("[[:punct:]]|[0-9]","",comments)
    comments <- tolower(comments)
    
    comments_string <- paste0(" ",comments," ")
    comments <- strsplit(comments," ")
    
    ## MAKE THE KEYWORD TABLE
    kw.tab.after <- table(comments)
    kw.tab.after <- as.data.frame(kw.tab.after)
    kw.tab.after$comments <- gsub("\n","",kw.tab.after$comments)
    
    ## REMOVE STOPWORDS
    stopwords <- gsub("[[:punct:]]","",stopwords("en"))
    kw.remove <- c()
    for(ii in 1:length(stopwords)){
      if(any(kw.tab.after$comments == stopwords[ii])){
        kw.remove <- c(kw.remove,which(kw.tab.after$comments == stopwords[ii]))
      }
    }
    
    count.after <- c()
    for(ii in 1:length(keywords)){
      count.after[ii] <- 0
      for(aa in 1:length(keywords[[ii]])){
        count.after[ii] <- count.after[ii] + str_count(comments_string,as.character(keywords[[ii]][aa]))
      }
    }

    countdf.after <- data.frame(count.after,kwList$Placeholder)
    colnames(countdf.after) <- c("kwCount","kw")

    countdf.after <- countdf.after[order(-countdf.after$kwCount),]

    if(any(countdf.after$kwCount == 0)){
      countdf.after <- countdf.after[-which(countdf.after$kwCount == 0),]
    }
    colnames(countdf.after) <- c("Frequency","Theme")
    
    countdf.after <- countdf.after[1:20,]
    
    kw.tab.after <- kw.tab.after[-kw.remove,]
    
    kw.tab.after <- kw.tab.after[order(-kw.tab.after$Freq),]
    
    kw.tab.after$comments <- gsub("\\s+","",kw.tab.after$comments)
    kw.tab.after <- kw.tab.after[-which(kw.tab.after$comments == ""),]
    
    kw.tab.after <- kw.tab.after[1:20,]
    
    colnames(kw.tab.after) <- c("Comment","Frequency")
    
    substr(kw.tab.after$Comment,1,1) <- toupper(substr(kw.tab.after$Comment,1,1))
    
    
    
    period_frequencies <- as.data.frame(table(db.period$COMMENT_CREATED))
    colnames(period_frequencies) <- c("Date","Frequency")
    
    
    
    dbCommentsPeriod <- db.period[order(as.numeric(as.character(db.period$COMMENT_LIKES)),decreasing = TRUE),]
    dbCommentsPeriod <- dbCommentsPeriod[1:10,c("COMMENT","COMMENT_LIKES","COMMENT_CREATED")]
    colnames(dbCommentsPeriod) <- c("Comment","Number of Likes","Comment Date")
    
    period.posts <- unique(db.period$POST)
    
    post.likes <- c()
    for(pp in 1:length(period.posts)){
      post.likes[pp] <- sum(as.numeric(db.period$COMMENT_LIKES[which(db.period$POST == period.posts[pp])]))
    }
    
    post.likes.df <- data.frame(period.posts,post.likes)
    post.likes.df <- post.likes.df[order(post.likes.df$post.likes,decreasing = TRUE),]
    colnames(post.likes.df) <- c("Post" ,"Likes")
    
    post.sources <- c()
    post.dates <- c()
    for(ii in 1:nrow(post.likes.df)){
      post.sources[ii] <- db.period$POST_FROM[which(db.period$POST == post.likes.df$Post[ii])[1]]
      post.dates[ii] <- substr(db.period$POST_CREATED[which(db.period$POST == post.likes.df$Post[ii])[1]],1,10)
    }
    
    post.likes.df <- data.frame(post.likes.df,post.sources,post.dates)
    
    post.likes.df <- post.likes.df[1:10,c(1,3,4)]
    
    colnames(post.likes.df) <- c("Post","Source","Date")
    
    post.likes.df$Post <- gsub("\\n"," ",as.character(post.likes.df$Post))
   
```

## Week Leading Up To Event - Keywords

```{r,echo = FALSE}

      p <- ggplot(data=kw.tab.before, aes(x = Comment, y = Frequency, group=1)) +
        geom_bar(stat = "identity",colour = "#42B874",fill = "#42B874") +
        theme(axis.ticks.x = element_blank()) +
        theme(axis.text.x = element_text(angle = 45, hjust = 1))

      p + labs("Week Previous")
      
```

\newpage

## Week Leading Up To Event - Themes

```{r,echo = FALSE}

p <- ggplot(data=countdf.before, aes(x = Theme, y = Frequency, group=1)) +
        geom_bar(stat = "identity",colour = "#42B874",fill = "#42B874") +
        theme(axis.ticks.x = element_blank()) +
        theme(axis.text.x = element_text(angle = 45, hjust = 1))

      p
      
```



\newpage

## Day Of Event - Keywords

```{r,echo = FALSE}
    
      p <- ggplot(data=kw.tab.day, aes(x = Comment, y = Frequency, group=1)) +
        geom_bar(stat = "identity",colour = "#42B874",fill = "#42B874") +
        theme(axis.ticks.x = element_blank()) +
        theme(axis.text.x = element_text(angle = 45, hjust = 1))
      
       p + labs("Day of Event")
      
```

\newpage

## Day Of Event - Themes

```{r,echo = FALSE}

p <- ggplot(data=countdf.day, aes(x = Theme, y = Frequency, group=1)) +
        geom_bar(stat = "identity",colour = "#42B874",fill = "#42B874") +
        theme(axis.ticks.x = element_blank()) +
        theme(axis.text.x = element_text(angle = 45, hjust = 1))

      p
      
```

\newpage

## Week After Event - Keywords

```{r,echo = FALSE}

      p <- ggplot(data=kw.tab.after, aes(x = Comment, y = Frequency, group=1)) +
        geom_bar(stat = "identity",colour = "#42B874",fill = "#42B874") +
        theme(axis.ticks.x = element_blank()) +
        theme(axis.text.x = element_text(angle = 45, hjust = 1))
      
     p + labs("Week After")

```

\newpage

## Week After Event - Themes

```{r,echo = FALSE}

p <- ggplot(data=countdf.after, aes(x = Theme, y = Frequency, group=1)) +
        geom_bar(stat = "identity",colour = "#42B874",fill = "#42B874") +
        theme(axis.ticks.x = element_blank()) +
        theme(axis.text.x = element_text(angle = 45, hjust = 1))
      
      p
      
```

\newpage

## Facebook Activity Over Period

```{r,echo = FALSE}
      p <- ggplot(data=period_frequencies, aes(x = Date, y = Frequency, group=1)) +
        geom_line(colour="#42B874", size=0.5) +
        geom_point(colour = "#504f51",size = 0.3) +
        theme(axis.ticks.x = element_blank(),axis.text.x = element_text(angle = 45, hjust = 1))
      
      p + labs("Facebook Activity Over Period")     

```

\newpage

## Top Posts During Period

```{r,echo = FALSE}

posts <- post.likes.df$Post

for(ii in 1:length(posts)){
  post <- strsplit(as.character(posts[ii])," ")[[1]]
  if(any(grepl("^http\\:\\/\\/",post))){
    post <- post[-grep("^http\\:\\/\\/",post)]
    post <- paste(post,collapse = " ")
    posts[ii] <- post
  }
}

post.likes.df$Post <- posts

row.names(post.likes.df) <- NULL
pander(post.likes.df,split.cells = c(40,15,15))
```

\newpage

## Top Comments During Period

```{r,echo = FALSE}
row.names(dbCommentsPeriod) <- NULL
pander(dbCommentsPeriod,split.cells = c(40,15,15))
```


    