---
output: 
  pdf_document:
      latex_engine: xelatex
mainfont: Verdana
theme: united
always_allow_html: yes

header-includes:
    - \usepackage{fancyhdr}
    - \usepackage{hyperref}
    - \usepackage{graphicx}
    - \hypersetup{linkcolor = blue}
    - \pagestyle{fancy}
    - \fancyhead[LE,RO]{© More Than Ideas}
    - \fancyhead[LE,LO]{\thepage}
---

\thispagestyle{empty}
\begin{center}
\includegraphics[width=10cm,height=10cm]{"www/morethanideas.jpeg"}
\end{center}

\vspace{4cm}

\begin{center}
{\Huge Aboriginal Attitudes}

\vspace{0.3cm}

{`r paste0(format(Sys.Date(),"%B %d"),", ", format(Sys.Date(),"%Y"))`}

\end{center}
\newpage

\tableofcontents

\newpage

#January

#### Frequency Trend

The following shows the frequency of comments for each day where data was gathered in the particular month. 

```{r,echo = FALSE}

month_str <- "01"

db.i <- db[which(substr(db$COMMENT_CREATED,6,7) == month_str),]

date_frequencies <- as.data.frame(table(db.i$COMMENT_CREATED))
colnames(date_frequencies) <- c("Date","Frequency")

p <- ggplot(data=date_frequencies, aes(x = Date, y = Frequency, group=1)) +
    geom_line(colour="#42B874", size=0.5) +
    geom_point(colour = "#504f51",size = 0.3) +
    theme(axis.ticks.x = element_blank()) + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
p
```

\newpage

#### Top Comments

```{r,echo = FALSE}

dbComments <- db.i[order(as.numeric(as.character(db.i$COMMENT_LIKES)),decreasing = TRUE),]
dbComments <- dbComments[1:5,c("COMMENT","COMMENT_LIKES","COMMENT_CREATED")]
colnames(dbComments) <- c("Comment","Likes","Date")
split.cells = c(40,15,15)
    
row.names(dbComments) <- NULL
pander(dbComments,row.names = FALSE,split.cells = c(40,15,15))
```

\newpage


#####Top Keywords

The following shows the top keywords that have been mentioned during the conversation for this period.

\vspace{0.5cm}

```{r,echo = FALSE}

source("dataProcessReporting.R")

p <- ggplot(data=kw.tab, aes(x = Comment, y = Frequency, group=1)) +
    geom_bar(stat = "identity",colour = "#42B874",fill = "#42B874") +
    theme(axis.ticks.x = element_blank(),axis.text.x = element_text(angle = 45, hjust = 1))
p
    
```

\newpage

####Top Themes

The following shows the frequency of themes that have been discussed during this period.

\vspace{0.5cm}

```{r,echo = FALSE}

p <- ggplot(data=countdf, aes(x = Theme, y = Frequency, group=1)) +
    geom_bar(stat = "identity",colour = "#42B874",fill = "#42B874") +
    theme(axis.ticks.x = element_blank()) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

p

```

\newpage

#February

#### Frequency Trend

The following shows the frequency of comments for each day where data was gathered in the particular month. 

```{r,echo = FALSE}

month_str <- "02"

db.i <- db[which(substr(db$COMMENT_CREATED,6,7) == month_str),]

date_frequencies <- as.data.frame(table(db.i$COMMENT_CREATED))
colnames(date_frequencies) <- c("Date","Frequency")

p <- ggplot(data=date_frequencies, aes(x = Date, y = Frequency, group=1)) +
    geom_line(colour="#42B874", size=0.5) +
    geom_point(colour = "#504f51",size = 0.3) +
    theme(axis.ticks.x = element_blank()) + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
p
```

\newpage


#####Top Comments

```{r,echo = FALSE}

dbComments <- db.i[order(as.numeric(as.character(db.i$COMMENT_LIKES)),decreasing = TRUE),]
dbComments <- dbComments[1:5,c("COMMENT","COMMENT_LIKES","COMMENT_CREATED")]
colnames(dbComments) <- c("Comment","Likes","Date")
split.cells = c(40,15,15)
    
row.names(dbComments) <- NULL
pander(dbComments,row.names = FALSE,split.cells = c(40,15,15))
```
\newpage


#####Top Keywords

The following shows the top keywords that have been mentioned during the conversation for this period.

\vspace{0.5cm}

```{r,echo = FALSE}

source("dataProcessReporting.R")

p <- ggplot(data=kw.tab, aes(x = Comment, y = Frequency, group=1)) +
    geom_bar(stat = "identity",colour = "#42B874",fill = "#42B874") +
    theme(axis.ticks.x = element_blank(),axis.text.x = element_text(angle = 45, hjust = 1))
p
    
```

\newpage

####Top Themes

The following shows the frequency of themes that have been discussed during this period.

\vspace{0.5cm}

```{r,echo = FALSE}

p <- ggplot(data=countdf, aes(x = Theme, y = Frequency, group=1)) +
    geom_bar(stat = "identity",colour = "#42B874",fill = "#42B874") +
    theme(axis.ticks.x = element_blank()) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

p

```

\newpage

#March

#### Frequency Trend

The following shows the frequency of comments for each day where data was gathered in the particular month. 

```{r,echo = FALSE}

month_str <- "03"

db.i <- db[which(substr(db$COMMENT_CREATED,6,7) == month_str),]

date_frequencies <- as.data.frame(table(db.i$COMMENT_CREATED))
colnames(date_frequencies) <- c("Date","Frequency")

p <- ggplot(data=date_frequencies, aes(x = Date, y = Frequency, group=1)) +
    geom_line(colour="#42B874", size=0.5) +
    geom_point(colour = "#504f51",size = 0.3) +
    theme(axis.ticks.x = element_blank()) + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
p
```
\newpage

#####Top Comments

```{r,echo = FALSE}

dbComments <- db.i[order(as.numeric(as.character(db.i$COMMENT_LIKES)),decreasing = TRUE),]
dbComments <- dbComments[1:5,c("COMMENT","COMMENT_LIKES","COMMENT_CREATED")]
colnames(dbComments) <- c("Comment","Likes","Date")
split.cells = c(40,15,15)
    
row.names(dbComments) <- NULL
pander(dbComments,row.names = FALSE,split.cells = c(40,15,15))
```
\newpage

#####Top Keywords

The following shows the top keywords that have been mentioned during the conversation for this period.

\vspace{0.5cm}

```{r,echo = FALSE}

source("dataProcessReporting.R")

p <- ggplot(data=kw.tab, aes(x = Comment, y = Frequency, group=1)) +
    geom_bar(stat = "identity",colour = "#42B874",fill = "#42B874") +
    theme(axis.ticks.x = element_blank(),axis.text.x = element_text(angle = 45, hjust = 1))
p
    
```

\newpage

####Top Themes

The following shows the frequency of themes that have been discussed during this period.

\vspace{0.5cm}

```{r,echo = FALSE}

p <- ggplot(data=countdf, aes(x = Theme, y = Frequency, group=1)) +
    geom_bar(stat = "identity",colour = "#42B874",fill = "#42B874") +
    theme(axis.ticks.x = element_blank()) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

p

```

\newpage

#April

#### Frequency Trend

The following shows the frequency of comments for each day where data was gathered in the particular month. 

```{r,echo = FALSE}

month_str <- "04"

db.i <- db[which(substr(db$COMMENT_CREATED,6,7) == month_str),]

date_frequencies <- as.data.frame(table(db.i$COMMENT_CREATED))
colnames(date_frequencies) <- c("Date","Frequency")

p <- ggplot(data=date_frequencies, aes(x = Date, y = Frequency, group=1)) +
    geom_line(colour="#42B874", size=0.5) +
    geom_point(colour = "#504f51",size = 0.3) +
    theme(axis.ticks.x = element_blank()) + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
p
```
\newpage

#####Top Comments

```{r,echo = FALSE}

dbComments <- db.i[order(as.numeric(as.character(db.i$COMMENT_LIKES)),decreasing = TRUE),]
dbComments <- dbComments[1:5,c("COMMENT","COMMENT_LIKES","COMMENT_CREATED")]
colnames(dbComments) <- c("Comment","Likes","Date")
split.cells = c(40,15,15)
    
row.names(dbComments) <- NULL
pander(dbComments,row.names = FALSE,split.cells = c(40,15,15))
```
\newpage

#####Top Keywords

The following shows the top keywords that have been mentioned during the conversation for this period.

\vspace{0.5cm}

```{r,echo = FALSE}

source("dataProcessReporting.R")

p <- ggplot(data=kw.tab, aes(x = Comment, y = Frequency, group=1)) +
    geom_bar(stat = "identity",colour = "#42B874",fill = "#42B874") +
    theme(axis.ticks.x = element_blank(),axis.text.x = element_text(angle = 45, hjust = 1))
p
    
```

\newpage

####Top Themes

The following shows the frequency of themes that have been discussed during this period.

\vspace{0.5cm}

```{r,echo = FALSE}

p <- ggplot(data=countdf, aes(x = Theme, y = Frequency, group=1)) +
    geom_bar(stat = "identity",colour = "#42B874",fill = "#42B874") +
    theme(axis.ticks.x = element_blank()) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

p

```


\newpage

#May

#### Frequency Trend

The following shows the frequency of comments for each day where data was gathered in the particular month. 

```{r,echo = FALSE}

month_str <- "05"

db.i <- db[which(substr(db$COMMENT_CREATED,6,7) == month_str),]

date_frequencies <- as.data.frame(table(db.i$COMMENT_CREATED))
colnames(date_frequencies) <- c("Date","Frequency")

p <- ggplot(data=date_frequencies, aes(x = Date, y = Frequency, group=1)) +
    geom_line(colour="#42B874", size=0.5) +
    geom_point(colour = "#504f51",size = 0.3) +
    theme(axis.ticks.x = element_blank()) + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
p
```
\newpage

#####Top Comments

```{r,echo = FALSE}

dbComments <- db.i[order(as.numeric(as.character(db.i$COMMENT_LIKES)),decreasing = TRUE),]
dbComments <- dbComments[1:5,c("COMMENT","COMMENT_LIKES","COMMENT_CREATED")]
colnames(dbComments) <- c("Comment","Likes","Date")
split.cells = c(40,15,15)
    
row.names(dbComments) <- NULL
pander(dbComments,row.names = FALSE,split.cells = c(40,15,15))
```
\newpage

#####Top Keywords

The following shows the top keywords that have been mentioned during the conversation for this period.

\vspace{0.5cm}

```{r,echo = FALSE}

source("dataProcessReporting.R")

p <- ggplot(data=kw.tab, aes(x = Comment, y = Frequency, group=1)) +
    geom_bar(stat = "identity",colour = "#42B874",fill = "#42B874") +
    theme(axis.ticks.x = element_blank(),axis.text.x = element_text(angle = 45, hjust = 1))
p
    
```

\newpage

####Top Themes

The following shows the frequency of themes that have been discussed during this period.

\vspace{0.5cm}

```{r,echo = FALSE}

p <- ggplot(data=countdf, aes(x = Theme, y = Frequency, group=1)) +
    geom_bar(stat = "identity",colour = "#42B874",fill = "#42B874") +
    theme(axis.ticks.x = element_blank()) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

p

```

\newpage


#June

#### Frequency Trend

The following shows the frequency of comments for each day where data was gathered in the particular month. 

```{r,echo = FALSE}

month_str <- "06"

db.i <- db[which(substr(db$COMMENT_CREATED,6,7) == month_str),]

date_frequencies <- as.data.frame(table(db.i$COMMENT_CREATED))
colnames(date_frequencies) <- c("Date","Frequency")

p <- ggplot(data=date_frequencies, aes(x = Date, y = Frequency, group=1)) +
    geom_line(colour="#42B874", size=0.5) +
    geom_point(colour = "#504f51",size = 0.3) +
    theme(axis.ticks.x = element_blank()) + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
p
```
\newpage

#####Top Comments

```{r,echo = FALSE}

dbComments <- db.i[order(as.numeric(as.character(db.i$COMMENT_LIKES)),decreasing = TRUE),]
dbComments <- dbComments[1:5,c("COMMENT","COMMENT_LIKES","COMMENT_CREATED")]
colnames(dbComments) <- c("Comment","Likes","Date")
split.cells = c(40,15,15)
    
row.names(dbComments) <- NULL
pander(dbComments,row.names = FALSE,split.cells = c(40,15,15))
```
\newpage

#####Top Keywords

The following shows the top keywords that have been mentioned during the conversation for this period.

\vspace{0.5cm}

```{r,echo = FALSE}

source("dataProcessReporting.R")

p <- ggplot(data=kw.tab, aes(x = Comment, y = Frequency, group=1)) +
    geom_bar(stat = "identity",colour = "#42B874",fill = "#42B874") +
    theme(axis.ticks.x = element_blank(),axis.text.x = element_text(angle = 45, hjust = 1))
p
    
```

\newpage

####Top Themes

The following shows the frequency of themes that have been discussed during this period.

\vspace{0.5cm}

```{r,echo = FALSE}

p <- ggplot(data=countdf, aes(x = Theme, y = Frequency, group=1)) +
    geom_bar(stat = "identity",colour = "#42B874",fill = "#42B874") +
    theme(axis.ticks.x = element_blank()) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

p

```

\newpage


#July

#### Frequency Trend

The following shows the frequency of comments for each day where data was gathered in the particular month. 

```{r,echo = FALSE}

month_str <- "07"

db.i <- db[which(substr(db$COMMENT_CREATED,6,7) == month_str),]

date_frequencies <- as.data.frame(table(db.i$COMMENT_CREATED))
colnames(date_frequencies) <- c("Date","Frequency")

p <- ggplot(data=date_frequencies, aes(x = Date, y = Frequency, group=1)) +
    geom_line(colour="#42B874", size=0.5) +
    geom_point(colour = "#504f51",size = 0.3) +
    theme(axis.ticks.x = element_blank()) + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
p
```
\newpage

#####Top Comments

```{r,echo = FALSE}

dbComments <- db.i[order(as.numeric(as.character(db.i$COMMENT_LIKES)),decreasing = TRUE),]
dbComments <- dbComments[1:5,c("COMMENT","COMMENT_LIKES","COMMENT_CREATED")]
colnames(dbComments) <- c("Comment","Likes","Date")
split.cells = c(40,15,15)
    
row.names(dbComments) <- NULL
pander(dbComments,row.names = FALSE,split.cells = c(40,15,15))
```
\newpage

#####Top Keywords

The following shows the top keywords that have been mentioned during the conversation for this period.

\vspace{0.5cm}

```{r,echo = FALSE}

source("dataProcessReporting.R")

p <- ggplot(data=kw.tab, aes(x = Comment, y = Frequency, group=1)) +
    geom_bar(stat = "identity",colour = "#42B874",fill = "#42B874") +
    theme(axis.ticks.x = element_blank(),axis.text.x = element_text(angle = 45, hjust = 1))
p
    
```

\newpage

####Top Themes

The following shows the frequency of themes that have been discussed during this period.

\vspace{0.5cm}

```{r,echo = FALSE}

p <- ggplot(data=countdf, aes(x = Theme, y = Frequency, group=1)) +
    geom_bar(stat = "identity",colour = "#42B874",fill = "#42B874") +
    theme(axis.ticks.x = element_blank()) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

p

```

\newpage


#August

#### Frequency Trend

The following shows the frequency of comments for each day where data was gathered in the particular month. 

```{r,echo = FALSE}

month_str <- "08"

db.i <- db[which(substr(db$COMMENT_CREATED,6,7) == month_str),]

date_frequencies <- as.data.frame(table(db.i$COMMENT_CREATED))
colnames(date_frequencies) <- c("Date","Frequency")

p <- ggplot(data=date_frequencies, aes(x = Date, y = Frequency, group=1)) +
    geom_line(colour="#42B874", size=0.5) +
    geom_point(colour = "#504f51",size = 0.3) +
    theme(axis.ticks.x = element_blank()) + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
p
```
\newpage

#####Top Comments

```{r,echo = FALSE}

dbComments <- db.i[order(as.numeric(as.character(db.i$COMMENT_LIKES)),decreasing = TRUE),]
dbComments <- dbComments[1:5,c("COMMENT","COMMENT_LIKES","COMMENT_CREATED")]
colnames(dbComments) <- c("Comment","Likes","Date")
split.cells = c(40,15,15)
    
row.names(dbComments) <- NULL
pander(dbComments,row.names = FALSE,split.cells = c(40,15,15))
```
\newpage

#####Top Keywords

The following shows the top keywords that have been mentioned during the conversation for this period.

\vspace{0.5cm}

```{r,echo = FALSE}

source("dataProcessReporting.R")

p <- ggplot(data=kw.tab, aes(x = Comment, y = Frequency, group=1)) +
    geom_bar(stat = "identity",colour = "#42B874",fill = "#42B874") +
    theme(axis.ticks.x = element_blank(),axis.text.x = element_text(angle = 45, hjust = 1))
p
    
```

\newpage

####Top Themes

The following shows the frequency of themes that have been discussed during this period.

\vspace{0.5cm}

```{r,echo = FALSE}

p <- ggplot(data=countdf, aes(x = Theme, y = Frequency, group=1)) +
    geom_bar(stat = "identity",colour = "#42B874",fill = "#42B874") +
    theme(axis.ticks.x = element_blank()) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

p

```

\newpage


#September

#### Frequency Trend

The following shows the frequency of comments for each day where data was gathered in the particular month. 

```{r,echo = FALSE}

month_str <- "09"

db.i <- db[which(substr(db$COMMENT_CREATED,6,7) == month_str),]

date_frequencies <- as.data.frame(table(db.i$COMMENT_CREATED))
colnames(date_frequencies) <- c("Date","Frequency")

p <- ggplot(data=date_frequencies, aes(x = Date, y = Frequency, group=1)) +
    geom_line(colour="#42B874", size=0.5) +
    geom_point(colour = "#504f51",size = 0.3) +
    theme(axis.ticks.x = element_blank()) + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
p
```
\newpage

#####Top Comments

```{r,echo = FALSE}

dbComments <- db.i[order(as.numeric(as.character(db.i$COMMENT_LIKES)),decreasing = TRUE),]
dbComments <- dbComments[1:5,c("COMMENT","COMMENT_LIKES","COMMENT_CREATED")]
colnames(dbComments) <- c("Comment","Likes","Date")
split.cells = c(40,15,15)
    
row.names(dbComments) <- NULL
pander(dbComments,row.names = FALSE,split.cells = c(40,15,15))
```
\newpage

#####Top Keywords

The following shows the top keywords that have been mentioned during the conversation for this period.

\vspace{0.5cm}

```{r,echo = FALSE}

source("dataProcessReporting.R")

p <- ggplot(data=kw.tab, aes(x = Comment, y = Frequency, group=1)) +
    geom_bar(stat = "identity",colour = "#42B874",fill = "#42B874") +
    theme(axis.ticks.x = element_blank(),axis.text.x = element_text(angle = 45, hjust = 1))
p
    
```

\newpage

####Top Themes

The following shows the frequency of themes that have been discussed during this period.

\vspace{0.5cm}

```{r,echo = FALSE}

p <- ggplot(data=countdf, aes(x = Theme, y = Frequency, group=1)) +
    geom_bar(stat = "identity",colour = "#42B874",fill = "#42B874") +
    theme(axis.ticks.x = element_blank()) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

p

```

\newpage


#October

#### Frequency Trend

The following shows the frequency of comments for each day where data was gathered in the particular month. 

```{r,echo = FALSE}

month_str <- "10"

db.i <- db[which(substr(db$COMMENT_CREATED,6,7) == month_str),]

date_frequencies <- as.data.frame(table(db.i$COMMENT_CREATED))
colnames(date_frequencies) <- c("Date","Frequency")

p <- ggplot(data=date_frequencies, aes(x = Date, y = Frequency, group=1)) +
    geom_line(colour="#42B874", size=0.5) +
    geom_point(colour = "#504f51",size = 0.3) +
    theme(axis.ticks.x = element_blank()) + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
p
```
\newpage

#####Top Comments

```{r,echo = FALSE}

dbComments <- db.i[order(as.numeric(as.character(db.i$COMMENT_LIKES)),decreasing = TRUE),]
dbComments <- dbComments[1:5,c("COMMENT","COMMENT_LIKES","COMMENT_CREATED")]
colnames(dbComments) <- c("Comment","Likes","Date")
split.cells = c(40,15,15)
    
row.names(dbComments) <- NULL
pander(dbComments,row.names = FALSE,split.cells = c(40,15,15))
```
\newpage

#####Top Keywords

The following shows the top keywords that have been mentioned during the conversation for this period.

\vspace{0.5cm}

```{r,echo = FALSE}

source("dataProcessReporting.R")

p <- ggplot(data=kw.tab, aes(x = Comment, y = Frequency, group=1)) +
    geom_bar(stat = "identity",colour = "#42B874",fill = "#42B874") +
    theme(axis.ticks.x = element_blank(),axis.text.x = element_text(angle = 45, hjust = 1))
p
    
```

\newpage

####Top Themes

The following shows the frequency of themes that have been discussed during this period.

\vspace{0.5cm}

```{r,echo = FALSE}

p <- ggplot(data=countdf, aes(x = Theme, y = Frequency, group=1)) +
    geom_bar(stat = "identity",colour = "#42B874",fill = "#42B874") +
    theme(axis.ticks.x = element_blank()) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

p

```

\newpage


#November

#### Frequency Trend

The following shows the frequency of comments for each day where data was gathered in the particular month. 

```{r,echo = FALSE}

month_str <- "11"

db.i <- db[which(substr(db$COMMENT_CREATED,6,7) == month_str),]

date_frequencies <- as.data.frame(table(db.i$COMMENT_CREATED))
colnames(date_frequencies) <- c("Date","Frequency")

p <- ggplot(data=date_frequencies, aes(x = Date, y = Frequency, group=1)) +
    geom_line(colour="#42B874", size=0.5) +
    geom_point(colour = "#504f51",size = 0.3) +
    theme(axis.ticks.x = element_blank()) + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
p
```
\newpage

#####Top Comments

```{r,echo = FALSE}

dbComments <- db.i[order(as.numeric(as.character(db.i$COMMENT_LIKES)),decreasing = TRUE),]
dbComments <- dbComments[1:5,c("COMMENT","COMMENT_LIKES","COMMENT_CREATED")]
colnames(dbComments) <- c("Comment","Likes","Date")
split.cells = c(40,15,15)
    
row.names(dbComments) <- NULL
pander(dbComments,row.names = FALSE,split.cells = c(40,15,15))
```
\newpage

#####Top Keywords

The following shows the top keywords that have been mentioned during the conversation for this period.

\vspace{0.5cm}

```{r,echo = FALSE}

source("dataProcessReporting.R")

p <- ggplot(data=kw.tab, aes(x = Comment, y = Frequency, group=1)) +
    geom_bar(stat = "identity",colour = "#42B874",fill = "#42B874") +
    theme(axis.ticks.x = element_blank(),axis.text.x = element_text(angle = 45, hjust = 1))
p
    
```

\newpage

####Top Themes

The following shows the frequency of themes that have been discussed during this period.

\vspace{0.5cm}

```{r,echo = FALSE}

p <- ggplot(data=countdf, aes(x = Theme, y = Frequency, group=1)) +
    geom_bar(stat = "identity",colour = "#42B874",fill = "#42B874") +
    theme(axis.ticks.x = element_blank()) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

p

```

\newpage


#December

#### Frequency Trend

The following shows the frequency of comments for each day where data was gathered in the particular month. 

```{r,echo = FALSE}

month_str <- "12"

db.i <- db[which(substr(db$COMMENT_CREATED,6,7) == month_str),]

date_frequencies <- as.data.frame(table(db.i$COMMENT_CREATED))
colnames(date_frequencies) <- c("Date","Frequency")

p <- ggplot(data=date_frequencies, aes(x = Date, y = Frequency, group=1)) +
    geom_line(colour="#42B874", size=0.5) +
    geom_point(colour = "#504f51",size = 0.3) +
    theme(axis.ticks.x = element_blank()) + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
p
```
\newpage

#####Top Comments

```{r,echo = FALSE}

dbComments <- db.i[order(as.numeric(as.character(db.i$COMMENT_LIKES)),decreasing = TRUE),]
dbComments <- dbComments[1:5,c("COMMENT","COMMENT_LIKES","COMMENT_CREATED")]
colnames(dbComments) <- c("Comment","Likes","Date")
split.cells = c(40,15,15)
    
row.names(dbComments) <- NULL
pander(dbComments,row.names = FALSE,split.cells = c(40,15,15))
```
\newpage

#####Top Keywords

The following shows the top keywords that have been mentioned during the conversation for this period.

\vspace{0.5cm}

```{r,echo = FALSE}

source("dataProcessReporting.R")

p <- ggplot(data=kw.tab, aes(x = Comment, y = Frequency, group=1)) +
    geom_bar(stat = "identity",colour = "#42B874",fill = "#42B874") +
    theme(axis.ticks.x = element_blank(),axis.text.x = element_text(angle = 45, hjust = 1))
p
    
```

\newpage

####Top Themes

The following shows the frequency of themes that have been discussed during this period.

\vspace{0.5cm}

```{r,echo = FALSE}

p <- ggplot(data=countdf, aes(x = Theme, y = Frequency, group=1)) +
    geom_bar(stat = "identity",colour = "#42B874",fill = "#42B874") +
    theme(axis.ticks.x = element_blank()) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

p

```














